Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5/2019 12:07
Update to inidividual representation (end of document)  14/5/2019 12:51

In the videogame industry many developers use a PCG style software that produces
raw images and designs used by other personnel to improve it and use it in order
to reduce the development cycles, and the productions cost. 
PCG as various focus areas that resolve around a video game, however in this paper 
the main focus is the \textit{Level design} area which as the objective to design 
the different areas of a game in wich a player can interact with, since in the 
angry birds video game a level is represented by a scene then the system will 
have to create the entities (birds and pigs) and objects (pieces) in it in order 
to create a playable level.

@@

>>>>

In the videogame industry many developers use a PCG style software that produces
raw images and designs used by other personnel to improve it and use it in order
to reduce the development cycles, and the productions cost. 
PCG as various focus areas that resolve around a video game, however in this paper 
the main focus is the \textit{Level design} area which as the objective to design 
the different areas of a game in which a player can interact with, since in the 
angry birds video game a level is represented by a scene then the system will 
have to create the entities (birds and pigs) and objects (pieces) in it in order 
to create a playable level.

@@

Finally figure \ref{layer12_combine} and figure \ref{layer123_combine} represent 
the way all the layers of an individual al combined to create a level after all 
the selection, combination and mutation operations, first in figure \ref{layer12_combine}
the composites layer is obtained from an individual, by a background process the 
width and height of all composites are obtained, then using the mask from the same 
individual the composites are placed in the order they are in their respective list 
(left to right in the level) in case a mask is not able to accommodate all the 
composites the remaining ones are not placed nor taken into account on the evaluation 
process, in the opposite case that there are not enough composites to fill a mask 
then the remaining areas are not taken into account as well, then in figure \ref{layer123_combine} 
the previous combination of layers is evaluated by cheking which placed composites 
can hold a pig in the center or on the top of it, then the pigs are placed in the 
same oreder the composites are placed (left to right) in the locations where one 
is able to be placed.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/layer12_combine.png}}
    \caption{Combination of composites layer and mask layer.}
    \label{layer12_combine}
\end{figure}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/layer123_combine.png}}
    \caption{Combination of figure \ref{layer12_combine} layers with pig layer.}
    \label{layer123_combine}
\end{figure}
